Generative Simplex Mapping: Nonlinear Endmember Extraction and Unmixing for Hyperspectral Imagery

### 2024-07-22 paper/paper.tex
Updates from Overleaf

\begin{figure}[H]
\includegraphics[width=0.85\columnwidth]{paper/figures/results-usgs/fit-comparison.pdf}
\caption{Comparison of GSM against NMF on simulated USGS dataset. \label{fig:usgs-fits}}
\end{figure}

@@

@@

\begin{figure}[H]
\includegraphics[width=0.85\columnwidth]{paper/figures/results-usgs/fit-comparison.pdf}
\caption{Comparison of GSM against NMF on simulated USGS dataset. \label{fig:usgs-fits}}
\end{figure}

\subsection{Nonlinear Mixing: Rhodamine Dye Plume}
\subsection{Nonlinear Mixing: Semi-supervised Analysis}

>>>>

\begin{figure}[H]
\includegraphics[width=\columnwidth]{paper/figures/methods/usgs/usgs-dataset.pdf}
\caption{Synthetic dataset from USGS spectra. \label{fig:usgs-data}}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=\columnwidth]{paper/figures/methods/robot-team/robot-team-overview.pdf}
\caption{Robot team dataset. \label{fig:robotteam-data}}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=0.85\columnwidth]{paper/figures/results/usgs/fit-comparison.pdf}
\caption{Comparison of GSM against NMF on simulated USGS dataset. \label{fig:usgs-fits}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\columnwidth]{paper/figures/results/usgs/extracted-endmembers.png}
\caption{Endmembers extracted using GSM for simulated USGS dataset with SNR$=20$. \label{fig:usgs-endmembers}}
\end{figure}

\subsection{Nonlinear Mixing: Rhodamine Dye Plume}

Exploratory data analysis: 
\begin{figure}[H]
\includegraphics[width=0.60\columnwidth]{paper/figures/results/robot-team/pca-variance.png}
\caption{Explained variance of PCA components for robot team dataset. A red horizontal line is superimposed on the plot indicating an explained variance of $1\%$. \label{fig:robot-team-pca}}
\end{figure}
